# Analysis {#sec-analysis}

```{r}
#| label: setup-analysis
#| include: false
here::i_am("manuscript/_quarto.yml")
source(here::here("manuscript", "_setup.R"))
```

Figures are built inline from pipeline targets with ggplot; they are never registered as targets or written to disk.
@fig-flipper-fit shows the example pattern, with data and fitted lines distinguished in the legend.

```{r}
#| label: fig-flipper-fit
#| fig-cap: "Body mass and flipper length by species"
#| fig-notes: "Palmer penguins, observations with recorded sex and body mass. Lines are species-specific linear fits."
ggplot() +
  geom_point(
    data = penguins_clean,
    aes(x = flipper_len, y = body_mass, color = species, shape = species),
    alpha = 0.5,
    size = 1
  ) +
  geom_line(
    data = analysis_flipper_fit$pred,
    aes(x = flipper_len, y = body_mass, color = species)
  ) +
  scale_species(name = NULL) +
  labs(x = "Flipper length (mm)", y = "Body mass (g)") +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.15, 0.9)
  )
```

Regression tables are built by `modelsummary()` from the model objects the
pipeline stores, not from a hand-assembled coefficient table (@tbl-flipper-fit).

```{r}
#| label: tbl-flipper-fit
#| tbl-cap: "Body mass on flipper length, by species"
modelsummary(
  analysis_flipper_fit$models,
  output = "tinytable",
  coef_map = c(flipper_len = "Flipper length (mm)", "(Intercept)" = "Constant"),
  gof_map = c("nobs", "r.squared"),
  stars = STARS,
  notes = notes_text("OLS by species on the estimation sample. Heteroskedasticity-robust standard errors in parentheses.")
) |>
  theme_mitex()
```
