---
title: "Note 01: Example workflow"
subtitle: "How a note freezes the theme, data, and results it needs"
author: Kazuharu Yanagimoto
date: "2026-07-20"
format:
  html:
    toc: true
    code-fold: true
    lightbox: true
bibliography: ../references.bib
---

```{r}
#| label: setup
#| include: false
# Self-contained: source this note's frozen setup, never tar_read() the pipeline.
source(here::here("notes", "01-example", "code", "setup.R"))
theme_set(theme_note())
```

## What this note demonstrates

Each note is a self-contained record of one round of trial and error.
The typical layout is `notes/NN-name/{index.qmd, code/, output/, data}`:

- `index.qmd` narrates the analysis and only reads CSVs from `output/`; prose language is up to you.
- `code/` holds the note's scripts: numbered computation scripts plus `setup.R`.
- `output/` holds the CSVs those scripts write. It is gitignored, because it is fully regenerable from the committed `code/`.
- `data` is a **symlink to `notes/data/`**, the shared home of note-stage datasets, so notes never duplicate data files.

Established results are promoted from the note into the main pipeline (`R/tar_*.R`), and the note stays behind as the record.

## A note is a frozen snapshot

A note never reads the live pipeline: there is no `tar_read()` or `tar_load()` anywhere in `notes/`.
Reading the pipeline from a note would quietly rewrite the record, because a note re-rendered next year would report whatever the pipeline says then, not what it said on the day the note was written.
Only `manuscript/` tracks the live pipeline, via `tar_load()` in `manuscript/_setup.R`.

The freeze has two halves, and the split matters:

- **Computation is frozen.** `code/01_body_mass.R` is the only place raw data is touched. It writes `output/*.csv`, and the qmd reads nothing else. Dropping `tar_read()` is not by itself enough: a note whose setup reads `data/` is still on live data and its findings still drift.
- **The theme is frozen too.** `code/setup.R` carries `theme_note()`, the palettes, the `scale_*()` helpers, and the table helpers, so the note keeps the look it was written with.

So `code/` is the record. `output/` is a cache, and `setup.R` regenerates it on a fresh clone.
The setup chunk above does nothing but `source()` that file and set the theme.

The mean body mass of the `r nrow(penguins_snapshot)` penguins in this note's snapshot is `r sprintf("%.2f", mean(penguins_snapshot$body_mass_kg))` kg.

```{r}
#| label: fig-body-mass
#| fig-cap: "Body mass by species and sex"
body_mass_summary |>
  ggplot(aes(x = species, y = mean_kg, color = sex, shape = sex)) +
  geom_pointrange(
    aes(ymin = mean_kg - 1.96 * sd_kg / sqrt(n), ymax = mean_kg + 1.96 * sd_kg / sqrt(n)),
    position = position_dodge(width = 0.3)
  ) +
  scale_sex(name = NULL) +
  labs(x = NULL, y = "Body mass (kg)") +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.85, 0.9)
  )
```

```{r}
#| label: tbl-body-mass
#| tbl-cap: "Mean body mass by species and sex"
body_mass_summary |>
  mutate(mean_kg = sprintf("%.2f", mean_kg)) |>
  select(Species = species, Sex = sex, N = n, `Mean (kg)` = mean_kg) |>
  tt(notes = notes_text("Sample restricted to penguins with observed sex and body mass."))
```

## Reading note-local data

Datasets that only exist at the note stage live in `notes/data/` and are reached through the `data` symlink in this folder.
Paths are resolved from the project root with `here::here()`, because the notes website renders every note with the repo root as the working directory.

Raw data is read in `code/`, never in the qmd:

```{r}
#| label: note-local-data
#| eval: false
# in code/02_something.R
raw <- readr::read_csv(here::here("notes", "01-example", "data", "my_extract.csv"))
# ... compute ...
readr::write_csv(result, file.path(O, "something.csv"))

# then, in the qmd
something <- rd("something.csv")
```
