---
title: "Note 01: Example workflow"
subtitle: "How a note consumes pipeline targets and note-local data"
author: Kazuharu Yanagimoto
date: "2026-07-20"
format:
  html:
    toc: true
    code-fold: true
    lightbox: true
bibliography: ../references.bib
---

```{r}
#| label: setup
#| include: false
library(targets)
library(dplyr)
library(ggplot2)
library(tinytable)
options(tinytable_html_mathjax = TRUE)

store <- here::here("_targets")
invisible(list2env(tar_read(fn_figure, store = store), envir = globalenv()))
theme_set(theme_proj())

penguins_clean <- tar_read(penguins_clean, store = store)
analysis_body_mass <- tar_read(analysis_body_mass, store = store)
```

## What this note demonstrates

Each note is a self-contained record of one round of trial and error.
The typical layout is `notes/NN-name/{index.qmd, code/, output/, data}`:

- `index.qmd` narrates the analysis; prose language is up to you.
- `code/` holds note-local scripts (heavy computation is run from here and cached to `output/`).
- `output/` holds generated artifacts and is gitignored.
- `data` is a **symlink to `notes/data/`**, the shared home of note-stage datasets, so notes never duplicate data files.

Established results are promoted from the note into the main pipeline (`R/tar_*.R`), and the note stays behind as the record.

## Reading pipeline targets

Targets from the main pipeline are read via the store, as in the setup chunk above.
The sample below uses the built-in example targets; the mean body mass of the `r nrow(penguins_clean)` penguins is `r sprintf("%.2f", mean(penguins_clean$body_mass_kg))` kg.

```{r}
#| label: fig-body-mass
#| fig-cap: "Body mass by species and sex"
analysis_body_mass |>
  ggplot(aes(x = species, y = mean_kg, color = sex, shape = sex)) +
  geom_pointrange(
    aes(ymin = mean_kg - 1.96 * sd_kg / sqrt(n), ymax = mean_kg + 1.96 * sd_kg / sqrt(n)),
    position = position_dodge(width = 0.3)
  ) +
  scale_sex(name = NULL) +
  labs(x = NULL, y = "Body mass (kg)") +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.85, 0.9)
  )
```

```{r}
#| label: tbl-body-mass
#| tbl-cap: "Mean body mass by species and sex"
analysis_body_mass |>
  mutate(mean_kg = sprintf("%.2f", mean_kg)) |>
  select(Species = species, Sex = sex, N = n, `Mean (kg)` = mean_kg) |>
  tt(notes = notes_text("Sample restricted to penguins with observed sex and body mass.")) |>
  theme_mitex()
```

## Reading note-local data

Datasets that only exist at the note stage live in `notes/data/` and are reached through the `data` symlink in this folder.

```{r}
#| label: note-local-data
#| eval: false
# The symlink makes note-local paths short and portable across notes:
raw <- readr::read_csv(here::here("notes", "01-example", "data", "my_extract.csv"))
```
