---
title: "Example Talk: Template Walkthrough"
subtitle: Example Seminar
date: 2026-07-20
format:
  touying-typst:
    include-in-header:
      text: |
        #import "@preview/touying-quarto-clean:0.2.0": *
        #import "@preview/cetz:0.5.2"
        #import "@preview/mitex:0.2.7": *
    theme-typst: clean-theme
---

```{r}
#| label: setup
#| include: false
# Self-contained: source this deck's frozen setup, never tar_load() the pipeline.
source(here::here("slides", "260720_example", "code", "setup.R"))
theme_set(theme_slide())
```

## Slide conventions

- Each deck is its own folder `slides/YYMMDD_venue/`, like a note: `index.qmd`, `code/`, `output/`, and a `data -> ../data` symlink to the shared `slides/data/`
- A deck is a **frozen snapshot**: it never reads the live pipeline with `tar_load`, so it compiles the same way years later regardless of how `R/` evolves
- Chunk labels use `plot-*` / `table-*` prefixes to suppress auto-captions

## Example figure

```{r}
#| label: plot-flipper
penguins_snapshot |>
  ggplot(aes(x = flipper_len, y = body_mass, color = species, shape = species)) +
  geom_point(alpha = 0.6) +
  scale_species(name = NULL) +
  labs(x = "Flipper length (mm)", y = "Body mass (g)") +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.85, 0.2)
  )
```
