---
title: "Example Talk: Template Walkthrough"
subtitle: Example Seminar
date: 2026-07-20
format:
  touying-typst:
    include-in-header:
      text: |
        #import "@preview/touying-quarto-clean:0.2.0": *
        #import "@preview/cetz:0.5.2"
        #import "@preview/mitex:0.2.7": *
    theme-typst: clean-theme
---

```{r}
#| label: setup
#| include: false
# Self-contained: source this deck's frozen setup, never tar_load() the pipeline.
# The slides project runs each deck with its own folder as the working
# directory (execute-dir: file), so paths here are relative to this folder.
source("code/setup.R")
theme_set(theme_slide())
```

# Conventions

## Slide conventions

- Each deck is its own folder `slides/YYMMDD_venue/`, like a note: `index.qmd`, `code/`, `output/`, and a `data -> ../data` symlink to the shared `slides/data/`
- A deck is a **frozen snapshot**, on the same terms as a note: it never reads the live pipeline with `tar_load`, so it compiles the same way years later regardless of how `R/` evolves
- Chunk labels use `plot-*` / `table-*` prefixes to suppress auto-captions

## Example figure

```{r}
#| label: plot-flipper
penguins_snapshot |>
  ggplot(aes(
    x = flipper_len,
    y = body_mass,
    color = species,
    shape = species
  )) +
  geom_point(alpha = 0.6) +
  scale_species(name = NULL) +
  labs(x = "Flipper length (mm)", y = "Body mass (g)") +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.85, 0.2)
  )
```

# Typst power: `mitex` and `cetz`

## Tables with math (`mitex`)

The species-level fit $m_i = \alpha + \beta\,\ell_i + \varepsilon_i$, where $m_i$ is body mass and $\ell_i$ flipper length.
`theme_mitex` turns the `$...$` in the header and notes into `mitex` calls, so LaTeX renders inside the Typst table.

```{r}
#| label: table-fit
species_fit |>
  mutate(
    alpha = sprintf("%.0f", alpha),
    beta = sprintf("%.1f", beta),
    r2 = sprintf("%.2f", r2)
  ) |>
  setNames(c("Species", "$\\hat\\alpha$ (g)", "$\\hat\\beta$ (g/mm)", "$R^2$")) |>
  tt(notes = "Estimates of $\\beta$ are the slope $\\partial m / \\partial \\ell$.")
```

## Diagrams with `cetz`

`cetz` draws vector graphics directly in Typst, so schematic figures need no image files.

```{=typst}
#align(center)[
#cetz.canvas(length: 1cm, {
  import cetz.draw: *
  let accent = rgb("#107895")
  let node(x, w, body) = {
    rect((x - w, -0.6), (x + w, 0.6), radius: 3pt, stroke: accent + 1pt)
    content((x, 0), body)
  }
  node(0, 1.3, [`data/`])
  node(4.4, 1.6, [`_targets`])
  node(8.8, 1.5, [outputs])
  line((1.3, 0), (2.8, 0), mark: (end: ">"), stroke: accent)
  line((6.0, 0), (7.3, 0), mark: (end: ">"), stroke: accent)
})
]
```

The pipeline turns tracked `data/` into a `_targets` store that the manuscript reads.
